\chapter{Patient experience survey}
\label{sec:patientsurvey}

\section{General user information}

\begin{enumerate}
\item Gender: $\square$ masculino $\square$ feminino
\item Age: 
\item Scholarly degree:
\begin{enumerate}[label=(\alph*)]
\item $\square$ Elementary school(1$^{o}$ ate 8$^{o}$  degree),
\item $\square$ Higg school (1$^{o}$  ate 3$^{o}$  year),
\item $\square$ Technical education,
\item $\square$ College
\item $\square$ Postgraduate
\end{enumerate}
\item Impariment(Examples):
\begin{enumerate}[label=(\alph*)]
\item $\square$ Monoplegia: paralysis in a limb;
\item $\square$ Hemiplegia: paralysis in half of the body;
\item $\square$ Paraplegia: paralysis from the waist down;
\item $\square$ Quadriplegia: paralysis of the neck down;
\item $\square$ Amputee: lack of a body member.
\item $\square$ Cerebral palsy: lesion of one or more areas of the central nervous system.
\end{enumerate}
\item  Impairment duration:
\end{enumerate}

\section{Patient profile}

\begin{enumerate}
\item What is your level of experience with the use of assistive technology?
\newline Excellent $\square$ Great $\square$ Good $\square$ Mean $\square$ Bad $\square$

\item What is your level of experience with the use of Internet browsers?
\newline Excellent $\square$ Great $\square$ Good $\square$ Mean $\square$ Bad $\square$
\item Do you know augmented reality?
\newline Yes $\square$ No $\square$
\item Do you have some limitations or difficulties for mobility?
\newline Yes $\square$ No $\square$ Let me know if is ``yes'':
\end{enumerate}

\section{System Assessment}
\begin{enumerate}
\item How was learning to use the system?
\newline Easier $\square$ Easy $\square$ Moderately $\square$ Quite complicated $\square$ Really difficult $\square$
\item How do you evaluate the graphical interface of the system?
\newline Excellent $\square$ Great $\square$ Good $\square$ Mean $\square$ Bad $\square$
\item It was easy to use the system?
\newline Easier $\square$ Easy $\square$ Moderately $\square$ Quite complicated $\square$ Really difficult $\square$
\item Does the system meet the navigation needs??
\newline Excellent $\square$ Great $\square$ Good $\square$ Mean $\square$ Bad $\square$
\item How do you consider the quality of the image displayed?
\newline Excellent $\square$ Great $\square$ Good $\square$ Mean $\square$ Bad $\square$
\item Do you feel immersed in the environment using the HMD?
\newline Strongly $\square$ A lot $\square$ Moderately $\square$ Not to much $\square$ Nothing $\square$
\item Do you think that the AR helped you during the session?
\newline Strongly $\square$ A lot $\square$ Moderately $\square$ Not to much $\square$ Nothing $\square$
\item How do you evaluate the processing time (response time)?
\newline Excellent $\square$ Great $\square$ Good $\square$ Mean $\square$ Bad $\square$
\item Do you think this modality has increased your ability for mobility?
\newline Strongly increased $\square$ A lot $\square$ Moderately $\square$ Not to much $\square$ Nothing $\square$
\item How do you assess your well being after training?
\newline Rested  $\square$ Little rested $\square$ Litle tired  $\square$ Tired $\square$  Exhausted  $\square$ 
\item Are you satisfied with the functionalities of the system?
\newline Excellent $\square$ Great $\square$ Good $\square$ Mean $\square$ Bad $\square$
\item Is the system doing what has been proposed correctly?
\newline Excellent $\square$ Great $\square$ Good $\square$ Mean $\square$ Bad $\square$

\item System Advantages:
\item System Disadvantages and difficulties using the system:
\item Notes suggestions:
\end{enumerate}



